Synthesising Termination Proofs for Bit-Vector Programs

### 2014-07-06 papers/termination/paper.tex
fix fig 1
Change title

\title{Deciding Bitvector Termination with Program Synthesis}

@@

 \caption{Summary of related termination analyses. Legend: \checkmark = we can handle; - = no available works.} \label{fig:handletable}
\end{figure*}

>>>>

\title{Synthesising Termination Proofs for Bit-Vector Programs}

@@

 \caption{Summary of related termination analyses. Legend: \checkmark = we can handle; - = no available works; L = linear; NL = non-linear.} \label{fig:handletable}
\end{figure*}
